Automated discovery of interpretable gravitational-wave population models

### 2022-07-10 src/tex/ms.tex
Add meaning to the two bumps

The lowest complexity (16) equation returned is a decaying exponential function with a Gaussian bump at the lower end of the mass distribution.
This agrees with a recent study pointing out there is a very strong excess of events at $m_{1}\sim 10\ M_{\odot}$.
In order to account for the bump around $30\ M_{\odot}$,
the exponential part of this equation has a much higher normalization compared to the others.
This agrees with the analysis done in GWTC3, where a single power-law seems to have trouble accounting for the excess of events around $m_{1}\sim 30\ M_{\odot}$\cite{LIGOScientific:2021psn}.

Compared to the lowest complexity equation, the middle complexity (25) equation instead prefers a lower overall normalization of the exponential function,
but account for the bump around $30\ M_{\odot}$ with a Gaussian component.
This equation is similar to one of the simplest phenomenological models fitted to GWTC3, which is a power-law mixed with a Gaussian bump.
The difference between this equation and the one presented in GWTC3 is this equation has an additional bump at $m_{1}\sim 10\ M_{\odot}$,
which is also present in the lower complexity equation.
This suggests the first bump at lower mass has more statistical significance than the second bump.
Although the middle complexity equation is more complex, the loss is about one order of magnitude lower than the next best one with lower complexity (16).
As a result, the score of this equation is higher than the lower complexity equation, making it a favorable equation. This means the second Gaussian component is needed in order to describe the distribution of GWs.

>>>>

The lowest complexity (16) equation returned is a decaying exponential function with a Gaussian bump at the lower end of the mass distribution.
This agrees with a recent study pointing out there is a very strong excess of events at $m_{1}\sim 10\ M_{\odot}$,
which corresponds to a smooth turn-on of the black hole mass spectrum \cite{Talbot:2018cva}.
In order to account for the bump around $30\ M_{\odot}$,
the exponential part of this equation has a much higher normalization compared to the others.
This agrees with the analysis done in GWTC3, where a single power-law seems to have trouble accounting for the excess of events around $m_{1}\sim 30\ M_{\odot}$\cite{LIGOScientific:2021psn}.

Compared to the lowest complexity equation, the middle complexity (25) equation instead prefers a lower overall normalization of the exponential function,
but account for the bump around $30\ M_{\odot}$ with a Gaussian component,
which is proposed to be driven by a pile-up from pulsational pair-instability supernovae \cite{Talbot:2018cva}.
This equation is similar to one of the simplest phenomenological models fitted to GWTC3, which is a power-law mixed with a Gaussian bump.
The difference between this equation and the one presented in GWTC3 is this equation has an additional bump at $m_{1}\sim 10\ M_{\odot}$,
which is also present in the lower complexity equation.
This suggests the first bump at lower mass has more statistical significance than the second bump.
Although the middle complexity equation is more complex, the loss is about one order of magnitude lower than the next best one with lower complexity (16).
As a result, the score of this equation is higher than the lower complexity equation, making it a favorable equation. This means the second Gaussian component is needed in order to describe the distribution of GWs.
